---
title: "Analysis For 1/24 Meeting"
author: "Mallory Barnes"
date: "January 23, 2017"
output: html_document
---

Analysis objectives for Dave M. one-on-one meeting 1/23/2017

1) Is there drought stress?


```{r, echo=FALSE}
data_file <- read.csv("C:/Users/Mallory/Dropbox/Drought_Expt_2016/All_with_more_licor_vars.csv")
library(ggplot2)
library(gridExtra)
data_file$date <- as.Date(data_file$date)

Big_Leaf <-subset(data_file, Genotype=="R-270")
Small_Leaf<-subset(data_file, Genotype=="52-276")

plot1 <- ggplot(Big_Leaf, aes(date, Water_Pot, colour=Plant_ID)) + geom_line(aes(group=Plant_ID))+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        ggtitle("Big Leaf - R-270")

plot2 <- ggplot(Small_Leaf, aes(date, Water_Pot, colour=Plant_ID)) + geom_line( aes(group=Plant_ID))+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        ggtitle("Small Leaf - 52-276")

grid.arrange(plot1, plot2, ncol=2)


```


2) Analyze Anet, gs, @ ambient (first A/Ci point) against Water Potential 
Correlation Between Anet and Water Potential 
```{r, echo=FALSE}
library(plyr)
func <- function(xx)
{
        COR=cor(xx$Water_Pot, xx$Photo)
        SIG=cor.test(xx$Water_Pot,xx$Photo)$p.value
        return(data.frame(COR, SIG))
        
}
func(data_file)
ddply(data_file, .(Genotype), func)
ddply(data_file, .(Plant_ID), func)
```
Correlation Between gs and Water Potential 
```{r, echo=FALSE}
library(plyr)
func <- function(xx)
{
        COR=cor(xx$Water_Pot, xx$Cond)
        SIG=cor.test(xx$Water_Pot,xx$Cond)$p.value
        return(data.frame(COR, SIG))
        
}
func(data_file)
ddply(data_file, .(Genotype), func)
ddply(data_file, .(Plant_ID), func)
```

```{r, echo=FALSE}
library(ggplot2)
library(gridExtra)
library(corrr)

print("Anet/Water Potential: Corr: 0.07063973,Significance: p=0.6049162")
print("Gs/Water Potential: Corr: -0.09283565,Significance: p=0.4961744")

Big_Leaf <-subset(data_file, Genotype=="R-270")
Small_Leaf<-subset(data_file, Genotype=="52-276")

plot1 <- ggplot(data_file, aes(Water_Pot, Cond, colour=Genotype)) + geom_point(aes(group=Genotype))+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        ggtitle("Conductance")

plot2 <- ggplot(data_file, aes(Water_Pot, Photo, colour=Genotype)) + geom_point(aes(group=Genotype))+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        ggtitle("Anet")

grid.arrange(plot1, plot2, ncol=2)
```


3) Compare instantaneous Ci/Ca Ratios (first point) against long term Ci/Ca ratio (from A/Ci curve)

```{r, echo=FALSE}
merged <- read.csv("Merged_data_to_analyze.csv")
library(ggplot2)
ggplot(merged, aes(Date.x, Vcmax, colour=Genotype)) + geom_smooth(method="lm", aes(group=Genotype))+
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

4) VI Relationships to Water Potential 

```{r, echo=FALSE}
"PRI"
func_PRI <- function(xx)
{
        COR=cor(xx$Water_Pot, xx$PRI)
        SIG=cor.test(xx$Water_Pot,xx$PRI)$p.value
        return(data.frame(COR, SIG))
        
}
func_PRI(data_file)
ddply(data_file, .(Genotype), func_PRI)
ddply(data_file, .(Plant_ID), func_PRI)

"NDVI"
func_NDVI <- function(xx)
{
        COR=cor(xx$Water_Pot, xx$NDVI)
        SIG=cor.test(xx$Water_Pot,xx$NDVI)$p.value
        return(data.frame(COR, SIG))
        
}
func_PRI(data_file)
ddply(data_file, .(Genotype), func_NDVI)
ddply(data_file, .(Plant_ID), func_NDVI)

"NDWI"
func_NDWI <- function(xx)
{
        COR=cor(xx$Water_Pot, xx$NDWI)
        SIG=cor.test(xx$Water_Pot,xx$NDWI)$p.value
        return(data.frame(COR, SIG))
        
}
func_NDWI(data_file)
ddply(data_file, .(Genotype), func_NDWI)
ddply(data_file, .(Plant_ID), func_NDWI)

```

Only significant correlation between NDWI and Water Potential in small leaf genotype

```{r, echo=FALSE}
Big_Leaf <-subset(data_file, Genotype=="R-270")
Small_Leaf<-subset(data_file, Genotype=="52-276")

plot1 <- ggplot(Big_Leaf, aes(Water_Pot, NDWI, colour=Plant_ID)) + geom_point(aes(group=Plant_ID))+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        ggtitle("Big Leaf R-270")

plot2 <- ggplot(Small_Leaf, aes(Water_Pot, NDWI)) + geom_point()+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) + geom_smooth(method="lm")+
        ggtitle("Small Leaf 52-276")

grid.arrange(plot1, plot2, ncol=2)
```



Correlation between Jmax and Water Potential

```{r, echo=FALSE}
library(plyr)
func <- function(xx)
{
        return(data.frame(COR = cor(xx$Water_Pot, xx$Jmax)))
}

ddply(merged, .(Genotype), func)
ddply(merged, .(Plant_ID.x), func)
```

Vcmax seems to be correlated with VPD, while Jmax isn't

Vcmax and VPD
```{r, echo=FALSE}
library(plyr)
func <- function(xx)
{
        return(data.frame(COR = cor(xx$VPD, xx$Vcmax)))
}

ddply(merged, .(Genotype), func)
ddply(merged, .(Plant_ID.x), func)
```

Jmax and VPD
```{r, echo=FALSE}
library(plyr)
func <- function(xx)
{
        return(data.frame(COR = cor(xx$VPD, xx$Jmax)))
}

ddply(merged, .(Genotype), func)
ddply(merged, .(Plant_ID.x), func)
```


