---
title: "Vcmax_Preliminary_Analysis"
author: "Mallory Barnes"
date: "September 19, 2016"
output: html_document
---


Preliminary analysis of Vcmax and Jmax from A_Ci curves from my B2 2016 Drought Experiment

Vcmax varied throughout the experiment:

```{r, echo=FALSE}
merged <- read.csv("C:/Users/rsstudent/Dropbox/Drought_Expt_2016/Merged_data_to_analyze.csv")
library(ggplot2)
library(gridExtra)
Big_Leaf <-subset(merged, Genotype=="R-270")
Small_Leaf<-subset(merged, Genotype=="52-276")

plot1 <- ggplot(Big_Leaf, aes(Date.x, Vcmax, colour=Plant_ID.x)) + geom_line(aes(group=Plant_ID.x))+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        ggtitle("Big Leaf - R-270")

plot2 <- ggplot(Small_Leaf, aes(Date.x, Vcmax, colour=Plant_ID.x)) + geom_line( aes(group=Plant_ID.x))+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        ggtitle("Small Leaf - 52-276")

grid.arrange(plot1, plot2, ncol=2)

```


So did Jmax - it has more of a clear downward trend: 

```{r, echo=FALSE}
merged <- read.csv("Merged_data_to_analyze.csv")
library(ggplot2)
library(gridExtra)
Big_Leaf <-subset(merged, Genotype=="R-270")
Small_Leaf<-subset(merged, Genotype=="52-276")

plot1 <- ggplot(Big_Leaf, aes(Date.x, Jmax, colour=Plant_ID.x)) + geom_line(aes(group=Plant_ID.x))+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        ggtitle("Big Leaf - R-270")

plot2 <- ggplot(Small_Leaf, aes(Date.x, Jmax, colour=Plant_ID.x)) + geom_line(aes(group=Plant_ID.x))+ theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        ggtitle("Small Leaf - 52-276")

grid.arrange(plot1, plot2, ncol=2)
```


Here's Vcmax grouped by Genotype (smoothed):

```{r, echo=FALSE}
merged <- read.csv("Merged_data_to_analyze.csv")
library(ggplot2)
ggplot(merged, aes(Date.x, Vcmax, colour=Genotype)) + geom_smooth(method="lm", aes(group=Genotype))+
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Here's Jmax grouped by Genotype (smoothed): 

```{r, echo=FALSE}
merged <- read.csv("Merged_data_to_analyze.csv")
library(ggplot2)
ggplot(merged, aes(Date.x, Jmax, colour=Genotype)) + stat_smooth(method="lm", aes(group=Genotype))+
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Variation in Jmax and Vcmax is not well-explaned by stress (pre-dawn water potential)

Correlation between Vcmax and Water Potential

```{r, echo=FALSE}
library(plyr)
func <- function(xx)
{
        return(data.frame(COR = cor(xx$Water_Pot, xx$Vcmax)))
}

ddply(merged, .(Genotype), func)
ddply(merged, .(Plant_ID.x), func)
```



Correlation between Jmax and Water Potential

```{r, echo=FALSE}
library(plyr)
func <- function(xx)
{
        return(data.frame(COR = cor(xx$Water_Pot, xx$Jmax)))
}

ddply(merged, .(Genotype), func)
ddply(merged, .(Plant_ID.x), func)
```

Vcmax seems to be correlated with VPD, while Jmax isn't

Vcmax and VPD
```{r, echo=FALSE}
library(plyr)
func <- function(xx)
{
        return(data.frame(COR = cor(xx$VPD, xx$Vcmax)))
}

ddply(merged, .(Genotype), func)
ddply(merged, .(Plant_ID.x), func)
```

Jmax and VPD
```{r, echo=FALSE}
library(plyr)
func <- function(xx)
{
        return(data.frame(COR = cor(xx$VPD, xx$Jmax)))
}

ddply(merged, .(Genotype), func)
ddply(merged, .(Plant_ID.x), func)
```

